Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2020-11-02 theory.tex
Pruning theory wording

Here the gas constants are molar mass, $M$, temperature $T$, universal gas constant, $R$,
and the pressure ratio, $x$ (typically $1000:1$).
This relationship is valid when $v_a > 380 \frac{\mathrm{m}}{\mathrm{s}}$.
Otherwise, the relationship can be approximated ${\frac{r_1}{r_2} \approx 0.534 \mid v_a \leq 380} \frac{\mathrm{m}}{\mathrm{s}}$.
In order to decompose the ratio into each individual radius, knowledge on one
of them is required. Glaser \cite{glaser.2008} states that $r_2$ typically ranges
from 96% to 99% the value of the inner centrifuge wall radius $a$. The exact
behavior of $r_2$ between these two values in operational conditions is unknown,
but a linear approximation can be made. It is assumed that $r_2$ is always at
the midpoint of these two extremes (i.e. $r_2 = 0.975 a$). Then, $r_1$ can be
found by simply multiplying this value by the ratio.

@@

In order to add clarity to the rest of this work, one will take the time to
define properly the different notation and the basic equation related to gaseous
centrifuge. The different enrichment factor, $\alpha$ (feed to product), $\beta$
(feed to tail) and $\gamma$(tail to product) are defined as the ratio of the
different abundance ($R = \frac{N}{1-N}$) where $N, N', N''$ respectively
correspond to the enrichment relative to the feed, the product and the tails:

@@

A symmetric cascade is a cascade where a stage is feed, $F$, with the tail, $T$, of the next
stage, the product, $P$, of the previous one, and for the cascade feeding stage
an external feed, $F_{ext}$, i.e. :

@@

\subsubsection{Symmetric Ideal Cascade}
The cascade is built as a symmetric ideal cascade, with no losses in the
separative work, which means that the tail assay of the next stage ($N''_{i+1}$)
is the as the product assay of the previous stage ($N'_{i-1}$), which can be
expressed as:
\begin{equation}
    \forall i~ N_{i} = N'_{i-1} = N''_{i+1}~ ~\Leftrightarrow~ ~\forall (i,j)~
    \alpha_{i} = \beta_{j}
\end{equation}

@@

The method used to design a symmetric ideal cascade starts with the feeding
stage. As all the enrichment factor are equal across all the cascade, the
feeding stage is used to determine those.
The feed assay of the feeding stage, $N_{0}$ is fixed by the external feed assay
provided as an input.

@@

From the mass conservation, $N = \theta N' + (1-\theta)N''$, and equations
\eqref{eq_alphabeta} it is possible to express $\beta$ as a function of the
feed abundance, $R$, the cut $\theta$ and $\alpha$:

@@

As illustrated on figure \ref{fig_a_m_b}, the $\theta$ value to ensure a ideal feeding
stage to the cascade range 0.45 0.525 depending on the feed assay.

@@

The design of the ideal symmetric cascade is performed through 2 steps.  First
one determines the configuration and number of stages, adding stages until the
product assay of the final stage is greater or equal the product targeted assay,
and similarly the tails assay is less or equal the tails desired assay.  This
determines the number of enriching and stripping stages as well as their
enrichment properties ($N_{i}$, $N'_{i}$, $N''_{i}$,$\theta_{i}$i).

>>>>

Here the gas constants are molar mass, $M$, temperature $T$, universal gas constant, $R$,
and the pressure ratio, $x$ (typically $1000:1$).
This relationship is valid when $v_a > 380 \frac{\mathrm{m}}{\mathrm{s}}$.
Otherwise, the relationship can be approximated $\{\frac{r_1}{r_2} \approx 0.534 \mid v_a \leq 380 \frac{\mathrm{m}}{\mathrm{s}}\}$.
In order to decompose the ratio into each individual radius, knowledge on one
of them is required. Glaser \cite{glaser.2008} states that $r_2$ typically ranges
from 96% to 99% the value of the inner centrifuge wall radius $a$. The exact
behavior of $r_2$ between these two values in operational conditions is unknown,
but a linear approximation can be made. It is assumed that $r_2$ is always at
the midpoint of these two extremes (i.e. $r_2 = 0.975 a$). Then, $r_1$ can be
found by simply multiplying this value by the ratio.

@@

The outputs of a centrifuge relative to its input can be described with ratios
of the abundance ($R = \frac{N}{1-N}$) where the feed, product, and tail are
$N, N', N''$ respectively. Enrichment factiors of $\alpha$ (feed to product),
$\beta$ (feed to tail), and $\gamma$ (tail to product) can then be defined:

@@

A symmetric cascade is a cascade where a stage's feed, $F$, with a tail, $T$, of the next
stage and product, $P$, of the previous one. For the cascade feeding stage
an external feed, $F_{ext}$:

@@

\subsubsection{Symmetric Ideal Cascade}
This model constructs cascades as symmetrical and ideal, with no losses in
separative work. This means that the tail assay of the next stage ($N''_{i+1}$)
is the product assay of the previous stage ($N'_{i-1}$), which can be
expressed as:

\begin{equation}
    \forall i~ N_{i} = N'_{i-1} = N''_{i+1}~ ~\Leftrightarrow~ ~\forall (i,j)~
    \alpha_{i} = \beta_{j}
\end{equation}

@@

The method used to design a symmetric ideal cascade starts with the feeding
stage. As all the enrichment factors are equal across all the cascade, the
feeding stage is used to determine all subsequent stages.
The feed assay of the feeding stage, $N_{0}$, is fixed by the external feed assay
provided as an input.

@@

From mass conservation, $N = \theta N' + (1-\theta)N''$, and equations
\eqref{eq_alphabeta} it is possible to express $\beta$ as a function of the
feed abundance, $R$, the cut $\theta$ and $\alpha$:

@@

As illustrated in Fig. \ref{fig_a_m_b}, $\theta$ ensures an ideal feeding
stage to the cascade ranges between 0.45 and 0.525, depending on the feed assay.

@@

The design of the ideal symmetric cascade is performed through 2 steps. First,
the configuration and number of stages is determined, adding stages until the
product assay of the final stage is greater or equal the product targeted assay,
and similarly the tails assay is less or equal the tails desired assay.  This
determines the number of enriching and stripping stages as well as their
enrichment properties ($N_{i}$, $N'_{i}$, $N''_{i}$,$\theta_{i}$).
